A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2021-06-17 Papers/Paper/manuscript.Rmd
more writing

```{r setup, include = FALSE}
 library("papaja")
 library(here)
 library(tidyverse)
library(patchwork)
 library(brms)
 library(lme4)
 library(tidybayes)
 library(mgcv)
 library(cowplot)
 library(gridExtra)
r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")
```
# Intro
It's remarkable how flexible we are when reading; while we do occasionally stumble when we read something unexpected, we often are able to read slightly unexpected things without a problem. However, these expectations shape how fast we read, even if we don't notice a stumble, unexpected words take longer to process as they force us to rebuild our burgeoning mental model of the sentence. Fortunately for fluent readers and unfortunately for studying language, this process of adjustment is very quick, which makes measures of reading time messy.

@@

An alternative method that seems to have superior localization is the Maze task, which adopts an unnatural way of reading to force incremental processing [@forsterMazeTaskMeasuring2009]. In the Maze task, participants see two words at a time, a correct word that continues the sentence, and a distractor which does not. Participants must choose the correct word, and their reaction time (RT) is the dependent measure. If participants make a mistake, the sentence discontinues. Theoretically, participants must fully integrate each word into the sentence in order to confidently select it. This idea is supported by studies finding strongly localized effects [@witzel12].

The downside of Maze is that materials are effort-intensive to construct because of the need to select infelicitious words as distractors for each spot of each sentence; this may explain why the Maze task was not widely adopted. 
@boyceMazeMadeEasy2020 demonstrate a way to automatically generate Maze distractors by using NLP language models to find words that are high-surprisal in the context of the target sentence. The quality of these A-Maze distractors is not up to that of hand-generated distractors, but @boyceMazeMadeEasy2020 found that materials with A-maze distractors had similar results to the hand-generated distractors from @witzel12. A-maze out performed a SPR control in detecting and localizing expected slowdown effects. @sloggettAmazeAnyOther also found that A-maze and G-maze distractors yielded similar results on a disambiguation paradigm.

@@

@@

## Participants
We recruited 100 participants from Amazon Mechanical Turk, and paid each participant 3.50 dollars, for roughly 20 minutes of work. We excluded data from those who did not report English as their native language, leaving `r data_filt %>% select(subject) %>% unique() %>% nrow()` participants.

@@

```{r}
package_list <- c("tidyverse","brms","rstan","papaja", "here",
                  "lme4", "mgcv", "tidybayes", "patchwork","cowplot", "gridExtra")
```

@@

To model the relationship between RT and word surprisal, we created a set of predictor variables of frequency, word length, and surprisals from three language models.  For length, we used the length in characters excluding end punctuation. For unigram frequency, we tokenized the training data from @gulordava18 and tallied up instances. We then used the log2 frequency of the expected occurances in 1 billion words as the model predictor, so higher values indicate higher log frequencies. We got per-word surprisals for each of 3 different language models: a Kneser-Ney smoothed 5-gram, GRNN [@gulordava], and Transformer-XL [@daiTransformerXLAttentiveLanguage2019a].  For all of these predictors, we consider both the predictor at the current word as well as lagged predictors from the previous word.

@@

For linear models, we centered all predictors. We used full mixed effects, including by-subject slopes and a per-word random intercept. We used weak priors (normal(1000,1000) for intercept, normal(0,500) for beta and sd, and lkj(1) for correlations). Models were run in BRM.

For model comparison, we fit models with only frequency and length as predictors, as well as models that also had one or more sources of surprisal. We centered all effects.

### TODO SPR!!!

@@

### TODO comparison with SPR !!!!

@@

As we can see in Table \@ref(tab:pre-error), we find large effects of surprisal and length, but minimal effects of frequency. These effects are larger than what is usually reported in other methods CITE, but this could be due to the overall slowness of the method. The lack of frequency effects is somewhat surprising, but consistent with CITE shain. Notably the coefficients for the lagged terms are small relative to the effects of surprisal and length of the current word.

@@

@@

Between auto-generating Maze distractors and the error-correction paradigm, Maze is a good complement to existing incremental processing methods. It localizes effects better that SPR does while showing similar patterns in terms of surprisal. In additon, despite the oddness of the task participants can succeed at it while understanding what they are reading. 
[summarize results] 
- error-correction paradigm
- test on natural stories
- it works

 While there are some differences, especially in scale, to that found with other incremental processing paradigms, we think this is a reason to explore more. Comparisons between methods could be very useful for identifying how task demands influence processing.

All the code is available, and we encourage researchers to consider trying out Maze if they think it's appropriate to their experiments. This opens up another area of research to being amenable to the new A-maze paradigm.

The Maze task might be espeically good for comparing with NNs because of the forced incrementality. While eventually we do want to figure out models of more natural reading, this might be a useful complement b/c we don't have to deal with nasty spillover.

Secondly, this error-correction compensates for some of the shortcomings of A-Maze identified in @boyceMazeMadeEasy2020; distractors might still cause participants to make unavoidable mistakes, but at least the still see the rest of the sentence and we get their data.  Whether this also solves the data loss problem from the researcher perspective within a sentence depends on whether post-mistake data are high-quality and trustworthy; this is a hard-to-assess question of potential interest.

Even if researchers exclude all post-mistake data from analysis, this process can still address the question of whether errors are due to inattentive participants or bad distractors (as discussed in @boyceMazeMadeEasy2020, section XX). When we have a participants selection for every word, we can easy calculate a per-word error rate for each participant, without having to address the censoring present in error-terminating Maze (where we can't know if a participant would have made more mistakes after the first; with error correction, we know how may more they did make). If participants are guessing, we'll see high per-word error rates, if the early distractors are bad, we'll see low per-word error rates (with errors concentrated at the start of the sentences).  This per-word error rate metric measures participants task accuracy, and allows us to exclude data from inattentive participants. This provides a convenient and clear-cut way of controlling data quality after the fact.

It also starts to reduce the perverse incentives. With error-terminates Maze, the fastest way to get through the task is to select randomly, and it's quite quick because mistakes skip you to the next sentence. With error-correction Maze, randomly jamming buttons takes more effort, but is still an effective strategy. [Footnote: In discussing this work, we recieved the suggestion that one way to disincentivize random clicking is to add a pause when a participant makes a mistake, forcing them to wait some short period of time (ex 500ms or 1 sec) before being able to correct their mistake. This seems like a promising improvement that could be worth implementing and testing.]

\newpage

>>>>

```{r setup, include = FALSE}
 library("papaja")
 library(here)
 library(tidyverse)
library(patchwork)
 library(brms)
 library(lme4)
 library(tidybayes)
 library(mgcv)
 library(cowplot)
 library(gridExtra)
library(broom.mixed)
library(tidymv)

r_refs("r-references.bib", append=F)
theme_set(theme_bw())
options(knitr.table.format = "pdf")
```
# Intro
It's remarkable how flexible we are when reading; while we do occasionally stumble when we read something unexpected, we often are able to read slightly unexpected things without a problem. However, these expectations shape how fast we read, even if we don't notice a stumble, unexpected words take longer to process as they force us to rebuild our burgeoning mental model of the sentence. Fortunately for fluent readers and unfortunately for studying language, this process of adjustment is very quick, which makes measures of reading time messy.

@@

An alternative method that seems to have superior localization is the Maze task, which adopts an unnatural way of reading to force incremental processing [@forsterMazeTaskMeasuring2009]. In the Maze task, participants see two words at a time, a correct word that continues the sentence, and a distractor which does not. Participants must choose the correct word, and their reaction time (RT) is the dependent measure. If participants make a mistake, the sentence discontinues. Theoretically, participants must fully integrate each word into the sentence in order to confidently select it. This idea is supported by studies finding strongly localized effects [@witzelComparisonsOnlineReading2012a].

The downside of Maze is that materials are effort-intensive to construct because of the need to select infelicitious words as distractors for each spot of each sentence; this may explain why the Maze task was not widely adopted. 
@boyceMazeMadeEasy2020 demonstrate a way to automatically generate Maze distractors by using NLP language models to find words that are high-surprisal in the context of the target sentence. The quality of these A-Maze distractors is not up to that of hand-generated distractors, but @boyceMazeMadeEasy2020 found that materials with A-maze distractors had similar results to the hand-generated distractors from @witzelComparisonsOnlineReading2012a. A-maze out performed a SPR control in detecting and localizing expected slowdown effects. @sloggettAmazeAnyOther also found that A-maze and G-maze distractors yielded similar results on a disambiguation paradigm.

@@

In addition to the texts, @futrellNaturalStoriesCorpus2020 released reading time data from a SPR study they ran. They recruited 181 participants, most of whom read 5 o the stories for a total of 988 story reads, or close to a million RT measures. After reading each story, each participant answered 6 binary-choice comprehension questions.

@@

## Participants
We recruited 100 participants from Amazon Mechanical Turk, and paid each participant $3.50 for roughly 20 minutes of work. We excluded data from those who did not report English as their native language, leaving `r data_filt %>% select(subject) %>% unique() %>% nrow()` participants.

@@

```{r}
package_list <- c("tidyverse","brms","rstan","papaja",
                  "lme4", "mgcv", "tidybayes")
```

@@

### Model specification
To model the relationship between RT and word surprisal, we created a set of predictor variables of frequency, word length, and surprisals from three language models.  For length, we used the length in characters excluding end punctuation. For unigram frequency, we tokenized the training data from @gulordava18 and tallied up instances. We then used the log2 frequency of the expected occurances in 1 billion words as the model predictor, so higher values indicate higher log frequencies. We got per-word surprisals for each of 3 different language models: a Kneser-Ney smoothed 5-gram, GRNN [@gulordava18], and Transformer-XL [@daiTransformerXLAttentiveLanguage2019].  For all of these predictors, we consider both the predictor at the current word as well as lagged predictors from the previous word.

@@

For linear models, we centered all predictors. We used full mixed effects, including by-subject slopes and a per-word-token random intercept. We used weak priors (normal(1000,1000) for intercept, normal(0,500) for beta and sd, and lkj(1) for correlations). Models were run in BRM.

For model comparison, we fit models with only frequency and length as predictors, as well as models that also had one or more sources of surprisal. We centered all effects. We included a random intercept for word identity, but no further random effects so the models would fit in LME4.

### Self-paced reading comparison

As a comparison we run similar models on the SPR corpus on Natural Stories [@futrellNaturalStoriesCorpus2020]. Data exclusions are the same as for A-maze; we do not make any exclusions based on participants comprehension accuracy. Generalized additive models are run with the same structure and predictors as for A-maze. Due to the size of the data, we were unable to run the full Bayesian mixed model; instead we estimate effect sizes uses a model with only random intercept for word identity fit in lmer, like that used for model comparison. We also run model comparison models similar to those described above.

@@

@@

As we can see in Table \@ref(tab:pre-error), we find large effects of surprisal and length, but minimal effects of frequency. These effects are larger than what is usually reported in other methods CITE, but this could be due to the overall slowness of the method. The lack of frequency effects is somewhat surprising, but consistent with @shainLargescaleStudyEffects2019. Notably the coefficients for the lagged terms are small relative to the effects of surprisal and length of the current word.

@@

## Comparison with SPR

```{r read_data}
d.raw.a <- here("Data/SPR/batch1_pro.csv") %>% 
  read_csv()

d.raw.b <- here("Data/SPR/batch2_pro.csv") %>% 
  read_csv()

offset=230 # following note in repo, we have to correct alignment on item 3 b/c an empty token was displayed

d.raw <- d.raw.a %>% union(d.raw.b) %>% 
  mutate(zone=if_else(item == 3 & zone > offset, zone - 3, zone - 2))

# spot check that this matches number wise with their processed words

```{r surprisals}

tokenization <- here("Data/SPR/all_stories.tok.txt") %>% 
  read_delim(delim="\t") %>% 
  mutate(Word_In_Story_Num=zone,
         Story_Num=item) %>%
  rename(Word=word)

#something is going on is story 2, sentence 4 His brother had blatantly peeked..." 
#they have it as "peaked", not sure what was displayed, but we can inner join
surprisals <- here("Data/SPR/natural_stories_surprisals2.rds") %>% 
  read_rds() %>% 
  inner_join(tokenization, by=c("Word_In_Story_Num", "Story_Num", "Word")) %>% 
  filter(ngram_token_count==1 & txl_token_count==1 & grnn_token_count==1) %>% 
  filter(!is.na(txl_surp) & !is.na(ngram_surp) & !is.na(grnn_surp) & !is.na(freq) & !is.na(length)) %>% 
    mutate(txl_center=txl_surp-mean(txl_surp, na.rm=T),
         ngram_center=ngram_surp-mean(ngram_surp, na.rm=T),
         grnn_center=grnn_surp-mean(grnn_surp, na.rm=T),
         freq_center=freq-mean(freq, na.rm=T),
         length_center=length-mean(length, na.rm=T))

past_word <- surprisals %>% 
  mutate(Word_In_Sentence_Num=Word_In_Sentence_Num+1) %>% 
  rename(past_txl=txl_surp, past_ngram=ngram_surp, past_grnn=grnn_surp, past_freq=freq, past_length=length,past_c_txl=txl_center, past_c_ngram=ngram_center, past_c_grnn=grnn_center, past_c_freq=freq_center, past_c_length=length_center) %>% 
  select(Story_Num,Sentence_Num, Word_In_Sentence_Num, starts_with("past")) %>% 
  inner_join(surprisals, by=c("Story_Num","Sentence_Num", "Word_In_Sentence_Num"))

```{r filter}

d.filter <- d.raw %>% 
  inner_join(past_word, by=c("zone", "item")) %>% 
  filter(RT>100 & RT<5000) %>% 
  filter(Word_In_Sentence_Num!=0)

#subset for testing
d.subset <- d.filter #%>% filter(Story_Num==1)
```

```{r pre_gam}
ngram_data <- d.subset %>% select(rt=RT, surprisal=ngram_surp, prev_surp=past_ngram, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            ) %>% mutate(model="5-gram")

grnn_data <- d.subset %>% select(rt=RT, surprisal=grnn_surp, prev_surp=past_grnn, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            )%>% mutate(model="GRNN")

txl_data <- d.subset %>% select(rt=RT, surprisal=txl_surp, prev_surp=past_txl, 
                                            freq=freq_center, len=length_center,
                                            prev_freq=past_c_freq, prev_len=past_c_length
                                            ) %>% mutate(model="TXL")

```{r gams, eval=F}
gam_ngram_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=ngram_data, method="REML")

gam_grnn_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=grnn_data, method="REML")

gam_txl_1 <- gam(rt ~ s(surprisal, bs="cr", k=20)+ te(freq, len, bs="cr")+s(prev_surp, bs="cr", k=20)+te(prev_freq, prev_len, bs="cr"), data=txl_data, method="REML")

```{r predict-gam, eval=F}

a <- get_gam_predictions(model=gam_ngram_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Current")
b <- get_gam_predictions(model=gam_ngram_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="5-gram", s="Previous")
c <- get_gam_predictions(model=gam_grnn_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Current")
d <- get_gam_predictions(model=gam_grnn_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="GRNN", s="Previous")
e <- get_gam_predictions(model=gam_txl_1, series=surprisal, series_length=100) %>% select(surprisal, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Current")
f <- get_gam_predictions(model=gam_txl_1, series=prev_surp, series_length=100) %>% select(surprisal=prev_surp, rt, CI_upper, CI_lower) %>% unique() %>% mutate(model="TXL", s="Previous")
all <- a %>% union(b) %>% union(c) %>% union(d) %>% union(e) %>% union(f) %>% write_rds("SPR_gam_predictions.rds")

```{r prep-brms}
d.for.lm <- d.subset %>%
  mutate(Word_ID=as_factor(str_c(Story_Num, Word_In_Story_Num, sep="_"))) %>% 
  mutate(subject=factor(WorkerId),
         rt=RT) %>% write_rds("for_brms.rds")
```

```{r}
#mean by subject for each word
d.byword <- d.for.lm %>% rename(word=Word) %>% 
  group_by(word, txl_center, ngram_center, grnn_center, freq_center, length_center,
                                        past_c_txl, past_c_ngram, past_c_grnn, past_c_freq, past_c_length, Word_ID) %>% 
  summarize(mean_rt=mean(rt))
```

ngram_only <- lmer(mean_rt ~ ngram_center + past_c_ngram + freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

grnn_only <- lmer(mean_rt ~ grnn_center + past_c_grnn + freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

txl_only <- lmer(mean_rt ~ txl_center + past_c_txl + freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

(ref:spr-gam-cap) GAM predictions of reaction time (RT) for SPR data from @futrellNaturalStoriesCorpus2020 as a function of either current word surprisal (top) or previous word surprisal (bottom). Density of data is shown along the x-axis.

```{r spr-gam, out.height="40%", fig.width=8, fig.height=3, fig.pos='t', fig.cap="(ref:spr-gam-cap)"}
all <- read_rds(here("Analysis/SPR_gam_predictions.rds"))

gam1 <-  ggplot(all, aes(x=surprisal, y=rt, ymin=CI_lower, ymax=CI_upper))+
  geom_line()+
  geom_ribbon(alpha=.3)+
  facet_grid(s~model)+
  coord_cartesian(ylim=c(300,400), xlim=c(0,28))+
  labs(x="Surprisal (bits)", y="Reaction Time (ms)")+
  theme(axis.ticks.x=element_blank(), 
        axis.title.x=element_blank(), 
        axis.text.x=element_blank(), 
        plot.margin=margin(t=0,r=0,b=0,l=0,unit="pt"))

dens2 <-   ggplot(all_data, aes(x=value))+
  geom_density(fill="gray",)+
  facet_grid(.~model)+
  labs(x="Surprisal (bits)", y="")+
  theme(strip.text.x=element_blank(),
        axis.text.y=element_blank(),
        panel.grid=element_blank(),
        axis.ticks.y=element_blank(), 
        plot.margin = unit(c(0, 0, 0, 0), "cm"))

p2 = align_plots(gam1, dens2, align = "v", axis="lr")
plot_grid(p2[[1]], p2[[2]], nrow=2, rel_heights = c(1, .3))

```{r spr-table}
ngram_only_tidy <- tidy(ngram_only, effects="fixed") %>% mutate(type="5-gram") %>% 
  mutate(term=str_replace(term, "ngram", "surp"))

txl_only_tidy <- tidy(txl_only, effects="fixed") %>% mutate(type="TXL") %>% 
   mutate(term=str_replace(term, "txl", "surp"))

grnn_only_tidy <- tidy(grnn_only, effects="fixed") %>% mutate(type="GRNN") %>% 
   mutate(term=str_replace(term, "grnn", "surp"))

all_tidy <- ngram_only_tidy %>% union(txl_only_tidy) %>% union(grnn_only_tidy) %>% 
  select(Term=term, estimate, std.error, type) %>% 
  mutate(Ci_high=estimate+1.96*std.error,
         Ci_low=estimate-1.96*std.error,
         Range=str_c(round(estimate,1)," [",round(Ci_low, 1),", ",round(Ci_high,1),"]")) %>% 
  select(Term, type, Range) %>% 
  pivot_wider(id_cols=Term, names_from=type, values_from=Range) %>% 
    mutate(Term=factor(Term, 
                        levels=c("(Intercept)", 
                                 "surp_center",
                                 "length_center",
                                 "freq_center",
                                 "freq_center:length_center",
                                 "past_c_surp",
                                 "past_c_length",
                                 "past_c_freq",
                                 "past_c_freq:past_c_length")
                                 )) %>% 
  arrange(Term) %>% 
  mutate(Term=c("Intercept", "Surprisal", "Length", "Frequency",
                   "Freq x Length", "Past Surprisal",
                  "Past Length", "Past Freq", "Past Freq x Length"))

knitr::kable(all_tidy, format="latex", position="t",caption="Predictions from fitted linear regression models. All terms were centered, but not rescaled. Units are in ms. Surprisal is per bit, length per character, and frequency per $log_2$ occurance per billion words.")
```

As a comparison, we ran the same types of models on the Self-Paced Reading data collected by @futrellNaturalStoriesCorpus2020. As shown in Figure \@ref(fig:spr-gam), there is a roughly linear but fairly flat relationship between RT and surprisal. Note that the y-axis is fairly narrow, and so the predicted effect of changes in surprisal is fairly small. This is confirmed by linear models (see Table \@ref(tab:spr-table)); note that due to the size of the data, these models were fit differently than the A-maze models due to computational constraints. Surprisal and length effects are evident for both the current and past word, but we do not see frequency effects. The effects are much smaller than for A-maze, although some of this may be due to noise from spillover from prior words or differences in model structure.

Lastly, we are interested to know which of the models is better at predicting human behavior data, and whether they are complementary. I fit a series of models including the frequency and length predictors, and some number of past or present surprisal sources. This allows us to tell whether different models of surprisal are "picking up" on different things that affect reading time.

We ran nested model comparison on the SPR data as well, and found that all sources of surprisal have predictive value, but the GRNN model provides the most benefit. Adding other models to GRNN is marginally beneficial, but TXL and N-gram together are more predictive than either alone.

```{r, eval=F}

no_surp <- lmer(mean_rt ~ freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

ngram_only <- lmer(mean_rt ~ ngram_center + past_c_ngram + freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

grnn_only <- lmer(mean_rt ~ grnn_center + past_c_grnn + freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

txl_only <- lmer(mean_rt ~ txl_center + past_c_txl + freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

all_surp <- lmer(mean_rt ~ ngram_center + past_c_ngram + 
                   grnn_center + past_c_grnn +
                   txl_center + past_c_txl +
                   freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

ngram_grnn <-  lmer(mean_rt ~ ngram_center + past_c_ngram + 
                   grnn_center + past_c_grnn +
                   freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

ngram_txl <-  lmer(mean_rt ~ ngram_center + past_c_ngram + 
                   txl_center + past_c_txl +
                   freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

grnn_txl <-  lmer(mean_rt ~ grnn_center + past_c_grnn +
                   txl_center + past_c_txl +
                   freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

no_lag <-  lmer(mean_rt ~ ngram_center +
                   grnn_center +
                   txl_center + 
                   freq_center*length_center+(1|word), data=d.byword)

no_surp_lag <-  lmer(mean_rt ~ ngram_center +  
                   grnn_center + 
                   txl_center +                    freq_center*length_center+past_c_freq*past_c_length+(1|word), data=d.byword)

  only_surp_lag <-  lmer(mean_rt ~ ngram_center + past_c_ngram + 
                   grnn_center + past_c_grnn +
                   txl_center + past_c_txl +
                   freq_center*length_center+(1|word), data=d.byword)
```

```{r, eval=F}
anova(txl_only, no_surp)
anova(grnn_only, no_surp)
anova(ngram_only, no_surp)

anova(ngram_grnn, ngram_only)
anova(ngram_grnn, grnn_only)
anova(ngram_txl, ngram_only)
anova(ngram_txl, txl_only)
anova(grnn_txl, grnn_only)
anova(grnn_txl, txl_only)
```

@@

We introduced a tweak to the paradigm for displaying Maze tasks that makes it useable for multi-sentence materials. In this error-correction Maze paradigm, participants read all the words because they can correct their mistakes and move on. We tested this method on the Natural Stories corpus, showing that, despite the oddness of the task, participants can read and understand a 1000 word story in this method. We additionally showed that the RTs generated in the Maze task show a linear relationship between the RT of a word and it's surprisal, but no relationship with the surprisal of the previous word. This provides additional evidence for the argument that the Maze task forces very incremental processing [@forsterMazeTaskMeasuring2009].

This extreme incrementality may make the Maze task a good target for comparisons between human RTs and predictions of surprisal from neural language models because spillover effects would not need to be considered as much. 
It shows broadly the same effects as other methods; however the differences in scale of suprisal effects and the lack of frequency effects detected here are a reason to explore more. Comparisons between different processing on the same materials could be useful for identifying how task demands influence language processing.

While the error-correction paradigm is crucial to running long materials, it also provides some benefits even on shorter materials when using A-maze with variable participant populations. The error-correction compensates for some of the shortcomings of A-Maze identified in @boyceMazeMadeEasy2020; poor distractors might still cause participants to make unavoidable mistakes, but they will still see the rest of the sentence, which may reduce frustration. Whether this also solves the data loss problem from the researcher perspective within a sentence depends on whether post-mistake data are high-quality and trustworthy; this is a hard-to-assess question of potential interest.

Even if post-mistake data is not analysed, it can be used to distinguish between errors due to inattentive participants or merely specific bad distractors early in the sentence. Researchers can calculate a per-word error rate for each participant; high per-word error rates are consistent with guessing, low error rates with errors clustered early the sentence are consistent with poor distractors. This per-word error rate metric measures participants task accuracy and provides a convenient and clear-cut way of controlling data quality after the fact.

Error-correction Maze also starts to reduce perverse incentives from the desire to complete the task quickly. With traditional Maze, clicking randomly will likely lead to a mistake, which will cause a participant to skip ahead to the next sentence. With error-correction Maze, randomly jamming buttons takes more effort, but is still faster than doing the task. In discussing this work, we received the suggestion that one way to disincentivize random clicking is to add a pause when a participant makes a mistake, forcing them to wait some short period of time (ex 500ms or 1 sec) before being able to correct their mistake. This seems like a promising improvement that could be worth implementing and testing.

Between the distractor auto-generation process introduced in @boyceMazeMadeEasy2020 and the error-correction paradigm introduced here, the Maze paradigm is now easy to use on a wide range of materials. The ease of use, large effects, and forced incrementality make Maze a good complement to existing incremental processing methods. We encourage researchers to consider Maze as an option for doing incremental processing work. 
\newpage
